Similar Article Detection Using Locality Sensitive Hashing Technique on Wikipedia\titlenote{This effort is part of the CMSC828G, Data Intensive Computing with MapReduce, class project.}

### 2013-05-08 article/sigproc-sp.tex
Removed unused graphics file.
Added some summarizing statistics about the cluster output.

\begin{figure}
\centering
\includegraphics[width=3.5in, keepaspectratio = true]{jac-ed-chart.png}
%\epsfig{file=jac-ed-chart.eps, height=4in, width=6in}
\caption{Jaccard Similarity vs. normalized edit distance.}
\label{jac-ed}
\end{figure}

@@

\section{Experiments and Discussion}
For this project, we performed several analyses to provide more insight into the occurence of duplicate sentences. In particular, we were interested in detecting the occurrence of templatification which is a precursor to the problem of finding factual drift between articles. \emph{Templatification} occurs when one sentence is an exact duplicate of another sentence, but the main topic has been changed by only a few pieces of key information having been modified. For example, it could be said that the following two sentences follow a particular \emph{template}.
\begin{itemize}[noitemsep,nolistsep]
\item Bush had an approval rating of 22\% by the end of his term in 2008.
\item Obama had an approval rating of 56\% by the end of his term in 2012.
\end{itemize}
From the perspective of editing/writing Wikipedia articles, this is a strong indicator that the author copied the original sentence and modified the relevant information to pertain to a different topic. What remains shared between both sentences though is the inherent structure.

@@

\begin{figure}
\centering
\includegraphics[width=3.5in, keepaspectratio = true]{clusterhistogram.png}
\caption{Histogram of Cluster Sizes (log scale).}
\label{clust}
\end{figure}

>>>>

\begin{figure}
\centering
\includegraphics[width=3.5in, keepaspectratio = true]{jac-ed-chart.png}
\caption{Jaccard Similarity vs. normalized edit distance.}
\label{jac-ed}
\end{figure}

@@

\section{Experiments and Discussion}

To test our application we ran the first four steps (up to but not including the final edit distance filtering pass) on a dump of current English-language Wikipedia articles (as of 5/2013) obtained from dumps.wikimedia.org. The dump is approximately 40G in size and contains 4,113,785 articles (after excluding certain non-article page types). After minhashing and deduplification, we found a total of 9,465,881 similar sentence pairs. After clustering these pairs, the total number of similar sentence clusters was 415,936, including 1,792,748 unique article/sentence pairs over 759,297 article titles. The total number of unique sentences over all cluster was 1,305,359.

Cluster sizes ranged from 2 to 28,008. (See Figure \ref{clust} for a breakdown of counts by cluster size.) Most sentence clusters are small, but the distribution of cluster exhibits a long tail. As a result, while 99\% of our clusters have size below or equal to 30, about 1/3 of the output sentence/article pairs fall into clusters with size greater than 30. One explanation for this distribution of sentences is the phenomenon we call ''tempatification,'' which we describe more in detail below.)

\subsection{Similar Sentence Types}

Sentence Clusters (without an Edit Distance Filter).

\begin{itemize}
\item Factual Drift
\item Templatification
\item References
\item Copy Editing
\end{itemize}

For this project, we performed several analyses to provide more insight into the occurence of duplicate sentences. In particular, we were interested in detecting the occurrence of templatification which is a precursor to the problem of finding factual drift between articles. \emph{Templatification} occurs when one sentence is an exact duplicate of another sentence, but the main topic has been changed by only a few pieces of key information having been modified. For example, it could be said that the following two sentences follow a particular \emph{template}.
\begin{itemize}[noitemsep,nolistsep]
\item Bush had an approval rating of 22\% by the end of his term in 2008.
\item Obama had an approval rating of 56\% by the end of his term in 2012.
\end{itemize}
From the perspective of editing/writing Wikipedia articles, this is a strong indicator that the author copied the original sentence and modified the relevant information to pertain to a different topic. What remains shared between both sentences though is the inherent structure.

@@

\begin{figure}
\centering
\includegraphics[width=3.5in, keepaspectratio = true]{clusterhistogram.png}
\caption{Histogram of Cluster Sizes (for cluster size $< 300$, log scale).}
\label{clust}
\end{figure}
